Grupo Bimbo Inventory Demand \\Data Science Report

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Models

\begin{itemize}
    \item $XGBoost$ Training: The XGBoost model was trained with parameters such as $n\_estimators=100$, $max\_depth=8$, $learning\_rate=0.1$, $subsample=0.8$, $colsample\_bytree=0.8$, and $random\_state=42$.
    \item $Random$ $Forest$ Training: The Random Forest model was trained with parameters including $n\_estimators=100$, $max\_depth=...$
\end{itemize}

>>>>

\begin{itemize}
    \item $XGBoost$ Training: The XGBoost model was trained with parameters such as $n\_estimators=200$, $max\_depth=8$, $learning\_rate=0.2$, $subsample=0.9$, $colsample\_bytree=0.8$, $n\_jobs=-1$, and $random\_state=42$.
    \item $Random$ $Forest$ Training: The Random Forest model was trained with parameters including $n\_estimators=110$, $min\_samples\_split=10$, $min\_samples\_leaf=5$, $n\_jobs=-1$, and $random\_state=42$.
\end{itemize}
